Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-13 paper/paper.tex
fixes

\section{ES6 design}
\label{sec:es6-design}
The EcmaScript is a language specification maintained by 
a committee called TC39 (Technical Committee) that follows 
standard rules proposed by ISO/ETC JTC 1 - 
Information Technology since 1996~\cite{es6-website}.
Along the year, a new version of EcmaScript (the latest version is ES2017) adds
new features and minor fixes for the language. \Fix{discutir mais sobre isso}

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries.
\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}
\Igor{seems like an API. They define the language behavior; grammar;
values to static variables; the methods for each "class"(Object)...
These irregularities appears on engine implementation, 
maybe an wrong if statement and so on.}
We found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that,
the function \CodeIn{Number.toPrecision(precision)}, in general,
if precision is defined the method returns a String 
containing the Number value represented either 
in decimal exponential notation or in decimal 
fixed notation~\cite{es6-toPrecision}. The Number object uses a 
property that the specification describes as approximately so when we use 
toPrecision with a bigger precision, the values of each engine may vary, this
could be considered as a case of incompatibility by engine design.}
In those cases, our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category.
\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
due the capacity of a fuzzer add an infinite repetition statement. We expected that
each test process can running utmost 5 seconds, if exceed this condition we stop 
the process and add a output message of a TIMEOUT error.}

@@

\Igor{
  We defined if an warning is in HI or LO group according to console output.
  The error stream in the output shows relevant informations that we can 
  process. The Figure~\ref{fig:hi-priority} shows an example of a warning 
  considered as a HI group, the stream output came from V8 engine. The error message 
  shows informations related to the assertion code (see at line 2) 
  that thows an Error exception. This case was considered as HI groups and after 
  several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
}

@@

% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function, 
%     typeof, return, throw, new, Error, if},
%   }
%   \begin{lstlisting}
% \end{lstlisting}
% \normalsize
% \caption{Warning captured as LO priority.}
% \label{fig:hi-priority}
% \end{figure}

@@

The first criterion focuses on actively maintained projects whereas
the second criterion focuses on popular cases. As we wanted to report
bugs, we also looked for project with public issue trackers.
Table~\ref{tab:engines} shows the engines we selected in this
study. We made an exception to the second criterion with
XS~\Fix{cite}. As the project is young, \Fix{created in xx.yy.zz}), we
thought there was insufficient time to obtain 1K stars for XS. We
still considered this project as it seems to be attracting interest
from the community\Fix{is this true?}. It is worth noting that we used
JSVU~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API\Fix{cite}. We noticed that some of the tests
we found depend on external libraries, which not all engines we use
(see Section~\ref{sec:methodology:engines}) support. We decided to
discard those. For example, many tests we found required a
nodejs\Fix{cite} runtime for execution. Overall, we considered the
test suites of three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines.

\Mar{vc. jah nao fala disto no paragrafo a seguir? se sim, junte os dois.}
We
implemented minor changes on test files with fixable file dependencies. For
example, some of the files used assertion functions defined in their
projects; we replaced those with our definitions.\Mar{not sure if this
  is a good example; why one would like to redefine assertion? why
  didn't you incorporate the assertion function to your infra?}

Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects. Overall, we found a total of
\totfiles{} JS files. It is worth noting that some projects use
distinct frameworks for testing and require external libraries to run
their testing suites. For these projects, we needed to make small
changes in the testing infrastructure to be able to uniformly run
tests in all engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}\Mar{apenas explique o que fez (mesmo
  que em portugues). isto nao deveria levar tempo que justifique
  escrever wip.}We aimed to use only the JS file with minor fixes to
support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

@@

    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & WebKit \\ 

>>>>

\section{ES6 design}
\label{sec:es6-design}
The EcmaScript is a language specification maintained by 
a committee called TC39 (Technical Committee) that follows 
standard rules proposed by ISO/ETC JTC 1 - 
Information Technology since 1996~\cite{es6-website}.
Every year, a new version of EcmaScript (the latest version is ES2017) adds
new features and minor fixes for the language. \Fix{discutir mais sobre isso}

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries.
\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}
\Igor{seems like an API. They define the language behavior; grammar;
values to static variables; the methods for each "class"(Object)...
These irregularities appears on engine implementation, 
maybe an wrong if statement and so on.}
We found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that,
the function \CodeIn{Number.toPrecision(precision)}, in general,
if precision is defined the method returns a String 
containing the Number value represented either 
in decimal exponential notation or in decimal 
fixed notation~\cite{es6-toPrecision}. The Number object uses a 
property that the specification describes as approximately so when we use 
toPrecision with a bigger precision, the values of each engine may vary, this
could be considered as a case of incompatibility by engine design.}
In those cases, our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only \Fix{12\%} of the reals bugs
we found originated from the LO category.
\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
due the capacity of a fuzzer add an infinite repetition statement. We expected that
each test process can running utmost 5 seconds, if exceed this condition we stop 
the process and add a output message of a TIMEOUT error.}

@@

\Igor{
  We defined if a warning is in HI or LO group according to console output.
  The error stream in the output shows relevant informations that we can 
  process. The Figure~\ref{fig:error-output} shows examples of HI and LO warning
  outputs based on the stream output came from Chakra engine. 
  % The error message shows informations related to the assertion code (see at line 2) 
  % that thows an Error exception. This case was considered as HI groups and after 
  % several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
}

% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function, 
%     typeof, return, throw, new, Error, if},
%   }
% \begin{lstlisting}

% \end{lstlisting}
% \normalsize
% \caption{Warning captured as HI priority.}
% \label{fig:hi-priority}
% \end{figure}

@@

% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function, 
%     typeof, return, throw, new, Error, if},
%   }
% \begin{lstlisting}
% function test() {
%   var buffer = new ArrayBuffer(64);
%   var view = new DataView(buffer);
%   view.setInt8 (0, 0x80);
%   -return view.getInt8(0) === -0x80;

%   // radamsa fuzzing
%   +return view.getInt8(-1770523502845470856862803727694) === -0x80;
%   }

%   if (!test())
%       throw new Error("Test Failed");
% \end{lstlisting}
% \normalsize
% \caption{Warning captured as HI priority.}
% \label{fig:hi-priority}
% \end{figure}

@@

The first criterion focuses on actively maintained projects whereas
the second criterion focuses on popular cases. As we wanted to report
bugs, we also looked for project with public issue trackers.
Table~\ref{tab:engines} shows the engines we selected in this
study. We made an exception to the second criterion with
XS~\Fix{cite}. As the project is young, created in Oct 2017, we
thought there was insufficient time to obtain 1K stars for XS. We
still considered this project as it seems to be attracting interest
from the community\Fix{is this true?}
\Igor{eu pensei sobre isso, acho que nao eh relevante colocar o XS sendo 
que ele eh uma engine para iot/embarcados, temos como exemplo o 
JerryScript que tambem tem o mesmo proposito e esta ha bem mais tempo
que ele. Por mim, utilizamos apenas o Jerry ou os dois (e compara-los ja que 
sao similares), oq vc acha?}. It is worth noting that we used
JSVU~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API\Fix{cite}. We noticed that some of the tests
we found depend on external libraries, which not all engines we use
(see Section~\ref{sec:methodology:engines}) support. We decided to
discard those. For example, many tests we found required a
nodejs\Fix{cite} runtime for execution. Overall, we considered the
test suites of three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines.
Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects. Overall, we found a total of
\totfiles{} JS files. It is worth noting that some projects use
distinct frameworks for testing and require external libraries to run
their testing suites. 
For these projects, we needed to make small
changes in the testing infrastructure to be able to uniformly run
tests in all engines. For example, some of the files does not use assertion 
functions defined in their projects; we replaced those with our definitions.
\Mar{not sure if this
  is a good example; why one would like to redefine assertion? why
  didn't you incorporate the assertion function to your infra?}
\Igor{sim, poderiamos fazer isso. Porem, lembro que alguns testcases por exemplo usam 
algo diferente de "assert", outras usam alguma funcao interna 
que apenas uma engine suporta. Eu posso analisar melhor aqui nossas seeds 
e ver um jeito global de resolver isso, como se fosse um "shell.js" da nossa 
ferramenta.}

@@

    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & LO & WebKit \\ 
